Regularising Lotka--Volterra Interaction Matrices by Species Grouping

### 2021-10-07 article.rnw
Extract the definition of the phylogeny forest style to its own document.
Add a pgfplotstable style for heatmaps.
Make knitr output as-is in the article document.

%Images
\usepackage{tikz}
\usepackage[edges]{forest}

@@

\forestset{
	phylogeny/.style={
		forked edges,
		delay={where content={}{shape=coordinate}{}}, %Make empty nodes leave no gaps.
		before typesetting nodes={
			where n children=0{tier=terminus}{},
		},
		for tree={
			grow=east,
			align=left,
			anchor=west,
			s sep=0, %Reduce the separation between the leaf nodes.
		}
	}
}

@@

>>>>

@@

\import{latex/}{forest-phylogeny}
\import{latex/}{pgfplotstable-color-cells}

@@

<<include=FALSE>>=
	knitr::opts_chunk$set(results = 'asis') #Text is grey without this.
@
